% FILE:     workshop (Master)
%
% LOCATION: /mhome/saam/sim/doc/workshop/
%
% AUTHOR:   saam
%
% DATE:     Sun Oct  1 18:59:58 MEST 2000
%
% MODIFICATION HISTORY:
%
%       $Log$
%       Revision 1.27  2003/08/14 14:31:29  kupper
%       still still
%
%       Revision 1.26  2003/08/14 14:29:41  kupper
%       still
%
%       Revision 1.25  2003/08/14 14:26:00  kupper
%       even more testing
%
%       Revision 1.24  2003/08/14 14:06:11  thiel
%          Automatically?
%
%       Revision 1.23  2003/08/14 13:50:11  kupper
%       still testing
%
%       Revision 1.22  2003/08/14 13:11:07  kupper
%       testing todo-automaking.
%
%       Revision 1.21  2003/08/14 12:45:45  kupper
%       just testing.
%
%       Revision 1.20  2003/08/14 09:52:53  thiel
%          Test.
%
%       Revision 1.19  2003/08/13 13:35:46  kupper
%       added new bug to utvscl.
%
%       Revision 1.18  2003/08/13 12:59:07  thiel
%          Small changes for test purpose.
%
%       Revision 1.17  2003/03/26 16:03:51  kupper
%       added two bugs for UTvScl in todo-list.
%
%       Revision 1.16  2001/11/27 14:25:25  thiel
%          FloatWeigh fulfilled.
%
%       Revision 1.15  2001/05/08 13:43:10  thiel
%          RealFileName can be turned off now.
%
%       Revision 1.14  2001/03/08 17:05:11  saam
%       moved several long fulfilled wishes and bugs to DONE list
%
%       Revision 1.13  2001/03/08 16:32:33  thiel
%          SimTime uses Console when you want it to.
%
%       Revision 1.12  2001/03/07 16:57:01  thiel
%          2 new entries, and one fulfilled.
%
%       Revision 1.11  2000/11/30 18:14:50  thiel
%           Fake/ForEach: SKEL and SEP no longer documeneted.
%
%       Revision 1.10  2000/10/17 08:41:12  saam
%       updated Help System section
%
%       Revision 1.9  2000/10/13 09:22:01  thiel
%           "WhoUses" doesnt work.
%
%       Revision 1.8  2000/10/12 16:29:45  thiel
%           Some new To Dos to do.
%
%       Revision 1.7  2000/10/11 16:21:30  thiel
%           DSim up to date.
%
%       Revision 1.6  2000/10/10 11:47:51  thiel
%           Some more To-Dos fulfilled.
%
%       Revision 1.5  2000/10/06 15:17:38  saam
%       new todo :(
%
%       Revision 1.4  2000/10/06 12:07:31  saam
%        new version including the, fri, wed
%
%       Revision 1.3  2000/10/03 16:16:51  saam
%       updated
%
%       Revision 1.2  2000/10/02 16:39:52  saam
%       todos from monday inserted
%
%       Revision 1.1  2000/10/02 16:35:10  saam
%       append one entry
%
%
%-
\documentclass[12pt]{article}


% Page Size & Formatting
\usepackage[a4paper,dvips]{geometry}           % page layout [twoside]
\setlength{\parindent}{0pt}                    % dont indent first paragraph
%\renewcommand{\baselinestretch}{2.0}          % double line spacing
%\usepackage{showlabels}                       % shows labels on side margin
\usepackage{showkeys}                          % prints label, ref, cite and bib keys
\usepackage{draftcopy}                         % displays draft in background of page (ps only!)
\usepackage{changebar}                         % changebars at margin via \cbstart ... \cbend (ps only!)


% References & Citations
\usepackage{lastpage}                          % access last page by \pageref{LastPage}
\usepackage[round]{natbib}                     % citestyle: Author (Year) by \cite or Author, Year with \citet
\usepackage{prettyref}                         % generates references like Figure/Table/Equation x, instead of x 
\newrefformat{fig}{Figure~\ref{#1}}
\usepackage{acronym}                           % make sure acronyms are spelled out at least once

% Version Control (rcs-latex must be installed!)
\usepackage{rcs}
\RCS $Header$
%\RCS $keyword$  % for keyword all RCS/CVS tags (like Header, Id) may be inserted; this line defines an tex command
%                % while the following command inserts it into the document
%\RCSkeyword
%                % there is also support for a formatted log history...

% Language
\usepackage[english,german]{babel}                    % set the language (german, english, ...)
\usepackage[latin1]{inputenc}                  % allow special characters directly in source

% Headers & Footers
\usepackage{fancyheadings}                     % allows individual header and footers
\pagestyle{fancy}
\lhead{\tiny\RCSHeader}                        % include path/name/date/RCS/CVS-version in header
\chead{}
\rhead{}
%\lfoot{}
%\cfoot{}
%\rfoot{}


% Fonts
%\usepackage{times}                            % use times, palatino, ...  ps-fonts instead of cm (dvi won't work!!)
%\usepackage{soul}                             % typeset text in spaced out way via \st{...} and more
\usepackage{SIunits}                           % use SI units by their name and produce upright greek symbols

        
\begin{document}

\begin{center}
{\Huge\textbf{Bugs, ToDos and Feature Requests}}\\[2cm]
Version: \$Id$ $\$ 
\end{center}

\section{Help System \& Documentation Header} 

\begin{itemize}
\item standards Makefile broken for non-saam environment
\item move Traps and Bugs into the standards document
\item \texttt{WhoUses} doesn't work and its wrapper calls routine with wrong path.
\item Parser confuses occasional \texttt{NAME::}--keywords with name
  of the routine given by the \texttt{NAME:} statement in the header.
\item The To Do--list on the WWW page needs to be updated by
  hand. Maybe this is not needed any longer, lets see\ldots
\end{itemize}



\section{Control}
\begin{itemize}
\item \texttt{console} fails, if xwindow id closed and a console command occurs
\item \texttt{console} should not be the son of !MH
\item \texttt{Video}: extension to save and restore arbitrary parameter structures
\end{itemize}


\section{Graphic}
\begin{itemize}
\item \texttt{UTvScl}:
\begin{itemize}
  \item Handling of 1-dim arrays is broken.
  \item Handling of arrays with trailing dimensions of 1 is broken.
  \item When /POLY is set, and only one positioning-argument is given,
    it is interpreted as the x-coordinate, and y defaults to zero.
    This is wrong, positions in the window should be counted in this
    case, see documentation of IDL's TV or POLY=0-behaviour.
\end{itemize}
\end{itemize}


\section{Methods}
\begin{itemize}
\item Nothing to do here at the moment.
\end{itemize}


\section{MIND}
\begin{itemize}
\item simulation and analysis routines save their evaluation parameters via \texttt{Video}s
\item allow deletion of unnecessary tags
\item external learning rules should display relevant information
\item display iteration time in \texttt{console} instead of terminal
\item Plotting input with /NASE option should be possible
\item Only plot changing inputs or use \texttt{PlotTvScl_Update}.
\end{itemize}



\section{Misc}
\begin{itemize}
\item \texttt{StrJoin}: remove or maintain due to IDL 3.6?
\item \texttt{Split}: bug when working with separator longer than 1 character
\item How can marburg specific extensions be included?
\item \texttt{XMatEdit}: obsolete 
\item \texttt{UOpenR} and partners should use IDLs streaming ZIP functionality.
WARNING: IDL is only able to zip since V5.3!
\end{itemize}




\section{Simulation Kernel}
\begin{itemize}
\item \texttt{saveDW} and \texttt{restoreDW} should work with \texttt{SDW}
\item initialize T2C on demand and in a separate function
\item extend \texttt{initDW} to work \texttt{SLOW} and \texttt{FAST} version
\item check the functionality of weight display routines, when T2C is missing
\item \texttt{N_Spikes} and \texttt{LayerMUA} are redundant. Current status: \texttt{N_Spikes} uses \texttt{LayerMUA} and generates warning.
\item \texttt{SetWeights} new version doesnt delete \texttt{!NONE} connections properly.
\end{itemize}



\section{Fulfilled ToDos}
\begin{itemize}
\item LExtrac: removed because obsolete [done, AT]
\item \texttt{DelayWeigh}: improvement in processing speed and memory consumption? NOPE [done]
\item Improve \texttt{MSetSDW} with \texttt{temporary}: no improvement [done, BAS]
\item \texttt{Console} ignores level keyword and outputs filename instead of procedure/function name [fixed, BAS]
\item \texttt{CAW}: doesn't work for Andreas, but \texttt{Widget_Control, /RESET} does.
\item \texttt{PeakPicker}: strange or wrong keyword handling. [fixed, AT]
\item Modify \texttt{foreach} to process multiple parameter variations synchronously. [done, MS & AT] 
\item Commit neuron type file [done, AT]
\item Subscribe Andreas Bruns to mailing list [done, AT] 
\item \texttt{DSim}: not up to date [done, AT]
\item Help System: \texttt{Keyword Parameters} heissen jetzt \texttt{Input Keywords} [MS]
\item Help System: Funktionen werden durch ein nachgestelltes rundes Klammerpaar angedeutet [MS]
\item Help System: Keywords werden komplett grossgeschrieben [MS]
\item Help System: Abtrennung von Keywords und Beschreibung durch ``::'' [MS]
\item Help System: show path to file in header display [MS]
\item Help System: header view also with currently edited [MS]
\item \texttt{FakeEach}: omit the skel keyword, or delete from documentation [done, AT]
\item let user parse arbitrary headers before checkin [done, MS]
\item Category: Kombination aus kurzen Keywords (feste Liste) zum Suchen, Syntax-Check? [done, MS]
\item directories unsorted in HyperHelp [done, MS]
\item remove headerdoc.pro and create link on mainpage to doc/header.pro [done, MS]
\item title for doc/header.pro is distorted [done, MS] 
\item allow \texttt{console} to log into a file, simultaneously [done, MS]
\item \texttt{PlotTvScl}: PS and NASE option broken [i think ruediger fixed this, MS] 
\item \texttt{PlotTvScl}: legend only approximately identical with actual coordinate system [see new routine PTVS, done, MS]
\item \texttt{SimTime}: make it work together with console [done, AT] 
\item \texttt{RealFileName}: marburg specific actions brake other systems [done, AT]
\item \texttt{floatWeigh}: commit, leave a message in \texttt{delayWeigh} to perform all changes in \texttt{floatWeigh} as well [FloatWeigh function is now included in DelayWeigh, AT].
\end{itemize}


\end{document}
